Self Regulation Ontology Retest Data Report

### 2017-11-10 code/SRO_Report.Rmd
jdm poster

ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 20, height = 8, units = "in", limitsize = FALSE)
```

>>>>

ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
```
